Signed Peripherality Functions for Multivariate Statistical Inference

### 2018-03-30 MS-new/1_Introduction.tex
new draft sent to anshu da

Consider a point $\bfx$ from some $\cX \subseteq \BR^p$, and the spatial sign function $\bfS : \cX \times \BR^p \mapsto \BR^p$, defined as
%
$$
\bfS (\bfx; \bfmu_x) = \frac{\bfx - \bfmu_x}{\| \bfx - \bfmu_x \|}
\BI ( \bfx \ne \bfmu_x ),
$$
%
where $\bfmu_x \in \BR^p$ is a fixed location parameter, $\BI(\cdot)$ is the 0/1 indicator function and $\|.\|$ is the euclidean norm. This is a generalization of the real-valued case of the indicator for whether a point $x \in \BR$ is to the right, left or at a scalar $\mu_{x} \in \BR$, and was first introduced by \cite{MottonenOja95}. Given a data matrix $\bfX = (\bfx_{1}, \ldots, \bfx_{n})^T$, a popular approach of using spatial signs in the literature has been to take spatial signs of the data points, i.e. $\bfS(\bfx_i)$, and use the matrix of signs as a proxy of $\bfX$ to formulate robust versions of location and scale problems  \citep{locantore99, OjaBook10,WangPengLi15}.

The spatial sign maps all data points to the surface of a $p$-dimensional unit sphere (see Figure~\ref{fig:rankplot}). While this transformation has its advantages (i.e. robustness), e.g. the eigenvectors remain the same while limiting the influence of outliers when the points are drawn from an elliptical distribution \citep{taskinen12}, valuable information is lost in the form of magnitudes of sample points. As a result, spatial sign-based procedures suffer from low efficiency. For example, eigenvector estimates obtained from the covariance matrix of spatial sign, which is called the Sign Covariance Matrix (SCM), are asymptotically inadmissible \citep{magyar14}- in the sense that there is an estimator (namely, Tyler's M-estimate of scatter \citep{tyler87}) that has uniformly lower asymptotic risk than the SCM.

\paragraph{}
To utilize the magnitude information of sample points, at the same time preserving the robustness property, we propose a general class weighted spatial sign functions. To this end, we first propose what we call a {\it peripherality function}.

@@

The peripherality function quantifies the relative position of $\bfx$ with respect to $\bfmu_{F}$, and condition (P) formalizes a general notion of centrality. A whole class of such functions can be defined from {\it Data Depth} functions \citep{zuo00}, which give the center-outward ranking of points in a multivariate dataset. Data depth has seen extensive use in the past decade, ranging from robust nonparametric classification \citep{jornsten04, ghosh05, dutta12, sguera14} to parametric estimation of means \citep{ZuoCuiHe04}, covariance matrices \citep{ZuoCui05} and sparse multivariate regression coefficients \citep{DuttaGenton17,MajumdarChatterjeeStat}. Peripherality functions can be defined as some inverse ranking based on data depth, and the concept of {\it outlyingness} associated with data depth is essentially same as what we use in this paper. However, traditional depth functions require a wider array of theoretical conditions \citep{zuo00} in addition to our condition (P), and a sizeable portion of methods we discuss do not require the use of depth functions {\it per se} to be implemented. %We use the term {\it peripherality} to keep track of the difference in application contexts and technical assumptions. As an additional objective of this paper, we discuss  some properties and uses of data-depth in real, separable Hilbert spaces.

@@

\begin{figure}[t]
	\captionsetup{singlelinecheck=off}
	\centering
		\includegraphics[height=6cm]{../Codes/ranks}
	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $ and (Right) their signed peripherality functions based on halfspace depth}
	\label{fig:rankplot}
\end{figure}

Our weighted sign vector, which we call the {\it signed peripherality} function, is now defined as the product of the spatial sign and transformed peripherality functions:
%
\begin{align}\label{eqn:rank}
\bfR (\bfx; \bfmu_x, \BF) = \bfS(\bfx, \bfmu_x). \kappa_P( P(\bfx, \BF)),
\end{align}
%
where $\kappa_P: \BR \rightarrow \BR$ is a monotone function. Its purpose is to either downweight or upweight the spatial sign of a point based on its peripherality with respect to a data cloud. As seen in the third panel of Figure~\ref{fig:rankplot}, $\bfR (\bfx; \bfmu_x, \BF)$ maps points {\it inside} a ball of finite radius, thus limiting the influence of outlying points {\it and} preserving the magnitude information of data points. In this paper, we demonstrate certain interesting applications of this multivariate rank transformation in robust statistical inference. Notice that for the trivial choice $P( \bfx; \BF) = \| \bfx - \bfmu_{F} \|$ and $\bfmu_x = \bfmu_F, \kappa_P(x)=x$, we get $\bfR (\bfx; \bfmu_x, \BF) = \bfx$. However, in this paper we illustrate how using the rank-transformed data in place of the original data points or their spatial signs leads to interesting robustness results for other choices of the peripherality functions.

The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector. Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95,HallinPaindaveine02} and \cite{Chernozhukov14}. Compared to them, the advantages of our signed peripherality function are two-fold: interpretability and flexibility. Firstly, as evident in Figure~\ref{fig:rankplot}, our rank transformation preserves the general shape of the data. In fact, if the map $\| \bfx \| \rightarrow P(\bfx, \BF)$ is one-one (given a fixed $\BF$), then it is possible to get back $\bfx$ from $\bfR (\bfx; \bfmu_x, \BF)$. It also provides an intuitive extension to any spatial sign-based methodology. Secondly, there is considerable scope of generalization within the present framework. Given any general inner product space, the definition of signed peripherality remains the same when euclidean norm is replaced by the norm induced by the inner product. Even within $\BR^p$, it is possible to generalize the ranking function in \eqref{eqn:rank} by adding separate transformations on the sign and peripherality functions to obtain alternate representations of the data in lower or higher dimensional spaces. However, we limit our discussion in this paper to the original formulation in \eqref{eqn:rank}.

In this paper, we assume $\BF$ to be an elliptical distribution. Following \cite{FangEtal90}, elliptical distributions can be formally defined here using their characteristic function:
%
\begin{Definition}
A $p$-dimensional random vector $\bfX$ is said to elliptically distributed if and only if there exist a vector $\bfmu \in \mathbb R^p$, a positive semi-definite matrix $\Omega \equiv \Sigma^{-1} \in \mathbb R^{p \times p}$ and a function $\phi: \mathbb R_+ \rightarrow \mathbb R$ such that the characteristic function $\bft \mapsto \phi_{\bfX - \bfmu} (\bft)$ of $\bfX - \bfmu$ corresponds to $\bft \mapsto \phi (\bft^T \Sigma \bft), \bft \in \mathbb R^p$.
\end{Definition}
%
\noindent The density function of an elliptically distributed random variable takes the form:
%
$$
h(\bfx; \bfmu, \Sigma) = |\Omega|^{1/2} g ((\bfx - \bfmu)^T \Omega (\bfx - \bfmu)),
$$
%
where $g$ is a non-negative scalar-valued density function that is continuous and strictly increasing, and is called the \textit{density generator} of the elliptical distribution. For ease of notation, we denote such a distribution by $\mathcal{E} (\bfmu, \Sigma, g)$.

@@

\paragraph{Organization of paper.}

\paragraph{Notation.}

>>>>

Consider a point $\bfx$ from some $\cX \subseteq \BR^p$, and the spatial sign function $\bfS : \cX \times \BR^p \mapsto \BR^p$, defined as
%
$$
\bfS (\bfx; \bfmu_x) = \frac{\bfx - \bfmu_x}{\| \bfx - \bfmu_x \|}
\BI ( \bfx \ne \bfmu_x ),
$$
%
where $\bfmu_x \in \BR^p$ is a fixed location parameter, $\BI(\cdot)$ is the 0/1 indicator function and $\|.\|$ is the euclidean norm. This is a generalization of the real-valued case of the indicator for whether a point $x \in \BR$ is to the right, left or at a scalar $\mu_{x} \in \BR$, and was first introduced by \cite{MottonenOja95}. Given a data matrix $\BX = (\bfx_{1}, \ldots, \bfx_{n})^T$, a popular approach of using spatial signs in the literature has been to take spatial signs of the data points, i.e. $\bfS(\bfx_i)$, and use the matrix of signs as a proxy of $\BX$ to formulate robust versions of location and scale problems  \citep{locantore99, OjaBook10,WangPengLi15}.

The spatial sign maps all data points to the surface of a $p$-dimensional unit sphere (see Figure~\ref{fig:rankplot}). While this transformation has its advantages (i.e. robustness), e.g. the eigenvectors remain the same while limiting the influence of outliers when the points are drawn from an elliptical distribution \citep{taskinen12}, valuable information is lost in the form of magnitudes of sample points. As a result, spatial sign-based procedures suffer from low efficiency. For example, eigenvector estimates obtained from the covariance matrix of spatial signs, which is called the Sign Covariance Matrix (SCM), are asymptotically inadmissible \citep{magyar14}- in the sense that there is an estimator (namely, Tyler's M-estimate of scatter \citep{tyler87}) that has uniformly lower asymptotic risk than the SCM.

\paragraph{}
To utilize the magnitude information of sample points, at the same time preserving the robustness property, we propose a general class weighted spatial sign functions. To this end, we first define what we call a {\it peripherality function}.

@@

Peripherality functions quantify the relative position of $\bfx$ with respect to $\bfmu_{F}$, and condition (P) formalizes a general notion of centrality. A whole class of such functions can be defined from {\it Data Depth} functions \citep{zuo00}, which give the center-outward ranking of points in a multivariate dataset. Data depth has seen extensive use in the past decade, ranging from robust nonparametric classification \citep{jornsten04, ghosh05, dutta12, sguera14} to parametric estimation of means \citep{ZuoCuiHe04}, covariance matrices \citep{ZuoCui05} and sparse multivariate regression coefficients \citep{DuttaGenton17,MajumdarChatterjeeStat}. Peripherality functions can be defined as some inverse ranking based on data depth, and the concept of {\it outlyingness} associated with data depth is essentially same as what we use in this paper. However, traditional depth functions require a wide array of theoretical conditions \citep{zuo00}, and a sizeable portion of methods we discuss do not require the use of depth functions {\it per se} to be implemented. %We use the term {\it peripherality} to keep track of the difference in application contexts and technical assumptions. As an additional objective of this paper, we discuss  some properties and uses of data-depth in real, separable Hilbert spaces.

@@

\begin{figure}[t]
	\captionsetup{singlelinecheck=off}
	\centering
		\includegraphics[width=\textwidth]{../Codes/signs_and_ranks}
	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $, (center) their spatial signs, and (right) signed peripherality functions based on halfspace depth.}
	\label{fig:rankplot}
\end{figure}

Our weighted sign vector, which we call the {\it signed peripherality} function, is now defined as the product of the spatial sign and transformed peripherality functions:
%
\begin{align}\label{eqn:rank}
\bfR (\bfx; \bfmu_x, \BF) = \bfS(\bfx, \bfmu_x). \kappa_P( P(\bfx, \BF)),
\end{align}
%
where $\kappa_P: \BR \rightarrow \BR$ is a monotone function. Its purpose is to either downweight or upweight the spatial sign of a point based on its peripherality with respect to a data cloud. As seen in the third panel of Figure~\ref{fig:rankplot}, $\bfR (\bfx; \bfmu_x, \BF)$ maps points {\it inside} a ball of finite radius, thus limiting the influence of outlying points {\it and} preserving the magnitude information of data points. In this paper, we demonstrate certain interesting applications of this multivariate rank transformation in statistical inference. Notice that for the trivial choice $P( \bfx; \BF) = \| \bfx - \bfmu_{F} \|$ and $\bfmu_x = \bfmu_F, \kappa_P(x)=x$, we get $\bfR (\bfx; \bfmu_x, \BF) = \bfx$. However, in this paper we illustrate how using the rank-transformed data in place of the original data points or their spatial signs leads to interesting robustness results for other choices of the peripherality functions.

The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector. Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95}, \cite{HallinPaindaveine02} and \cite{Chernozhukov17}. Compared to them, the advantages of our signed peripherality function are two-fold: interpretability and flexibility. Firstly, as evident in Figure~\ref{fig:rankplot}, our rank transformation preserves the general shape of the data. In fact, if the map $\| \bfx \| \rightarrow P(\bfx, \BF)$ is one-one (given a fixed $\BF$), then it is possible to get back $\bfx$ from $\bfR (\bfx; \bfmu_x, \BF)$. It also provides an intuitive extension to any spatial sign-based methodology. Secondly, there is considerable scope of generalization within the present framework. Given any general inner product space, the definition of signed peripherality remains the same when euclidean norm is replaced by the norm induced by the inner product. Even within $\BR^p$, it is possible to generalize the ranking function in \eqref{eqn:rank} by adding separate transformations on the sign and peripherality functions to obtain alternate representations of the data in lower or higher dimensional spaces. However, we limit our discussion in this paper to the original formulation in \eqref{eqn:rank}.

We assume $\BF$ to be an elliptical distribution. Following \cite{FangEtal90}, elliptical distributions can be formally defined here using their characteristic function:
%
\begin{Definition}
A $p$-dimensional random vector $\bfX$ is said to elliptically distributed if and only if there exist a vector $\bfmu \in \mathbb R^p$, a positive semi-definite matrix $\Omega \equiv \Sigma^{-1} \in \mathbb R^{p \times p}$ and a function $\phi: \mathbb R_+ \rightarrow \mathbb R$ such that the characteristic function $\bft \mapsto \phi_{\bfX - \bfmu} (\bft)$ of $\bfX - \bfmu$ corresponds to $\bft \mapsto \phi (\bft^T \Sigma \bft), \bft \in \mathbb R^p$.
\end{Definition}
%
\noindent The density function of an elliptically distributed random variable takes the form:
%
$$
h(\bfx; \bfmu, \Sigma) = |\Omega|^{1/2} g ((\bfx - \bfmu)^T \Omega (\bfx - \bfmu)),
$$
%
where $g$ is a non-negative scalar-valued density function that is continuous and strictly increasing, and is called the \textit{density generator} of the elliptical distribution. For ease of notation, we denote such a distribution by $\mathcal{E} (\bfmu, \Sigma, g)$.

@@

\paragraph{Organization of paper.} We start by elaborating on the use of weighted spatial signs in the problem of estimating or testing for the location parameter $\bfmu$ of $\BF$ in Section~\ref{section:LocSection}. Specifically, we use the signed peripherality vectors in \eqref{eqn:rank} to propose more efficient versions of the spatial median \citep{brown83, Chaudhuri96} and the high-dimensional testing procedure of \cite{WangPengLi15}. In Section~\ref{section:dcmSection}, we take inverse depth functions \citep{MajumdarChatterjeeStat} as our weights, and lay out a framework to estimate the different components of the covariance matrix $\Sigma$- namely, its eigenvectors (i.e. principal component analysis (PCA)), eigenvalues and $\Sigma$ itself. The two subsequent sections are devoted to the applications of the robust PCA method in Sections~\ref{section:LocSection} and \ref{section:dcmSection}. In Section~\ref{section:sdrSection} we use the robust estimates of $\bfmu$ and eigenvectors of $\Sigma$ in a supervised learning problem, while in Section~\ref{section:fpcaSection} we propose a robust functional PCA based on our methodology. We conclude with a discussion in \ref{section:Conclusion}. The appendix contains auxiliary theoretical results and proofs.

\paragraph{Notation.} We denote vectors $\bfa \in \BR^A$ by bold small letters, matrices $\BA \in \BR^{A \times A}$ by blackboard bold or greek capital letters, vector-valued random variables $\bfA$ by bold capital letters and their elements by small letters. For the vector $\bfa$, we denote euclidean norm and $\ell_1$-norm by $\|a\|$ and $\| a\|_1$, respectively. We denote expectations by $\BE(\cdot)$, the variance of a scalar random variable or covariance of a vector-valued random variable by $\BV(\cdot)$, and the covariance of two scalar random variables by $\BC(\cdot)$. Asymptotic variances (or covariance matrices) and covariances are denoted by $A\BV(\cdot)$ and $A\BC(\cdot)$, respectively. Sample variances are denoted by $\BS(\cdot)$, i.e. $\BS(\bfa) = \bfa^T \bfa /a - (\sum_{i=1}^A a_i/a)^2$ and $\BS(\BB) = \BB^T \BB/B - \bar \bfb \bar \bfb^T$ for $\BB = (\bfb_1, \ldots, \bfb_B)^T \in \BR^{B \times B_1}$, $\bar \bfb = \sum_{i=1}^B \bfb_i/B$.

### 2018-03-30 MS-new/2_Location.tex
main paper v1 done, proofs and intro remain
new draft sent to anshu da

\vspace{1em}
\noindent{\bf (A1)} The weights are affine invariant, i.e.
%
$$
w(\bfA \bfx + \bfb, \bfA \BF + \bfb) = w(\bfx, \BF),
$$
%
for any $\bfb \in \BR^p$ and full rank matrix $\bfA \in \BR^{p \times p}$.

@@

A straightforward use of weighted signs in a location problem is to construct an outlier-robust alternative to the Hotelling's $T^2$ test using their sample mean vector and covariance matrix. Formally, this means testing for $H_0: \bfmu = {\bf 0}_p$ vs. $H_1:\bfmu \neq {\bf 0}_p$  based on the test statistic:
%
$$
T_{n,w} = n \bar\bfX_w^T ( \BV \BX_w)^{-1} \bar\bfX_w,
$$
%
({\colrbf define $\BX_w$}) with $\bar\bfX_w = \sum_{i=1}^n \bfX_{w,i}/n$ and $\bfX_{w,i} = w(\bfX_i ) \bfS (\bfX_i)$ for $i=1,2,...,n$. However, the following holds true for this weighted sign test:
%
\begin{Proposition}\label{proposition:SignTest}
Consider $n$ random variables $Z = (\bfZ_1,...,\bfZ_n)^T$ distributed independently and identically as $\mathcal{E}( \bfmu, k \bfI_p, g); k \in \mathbb R$, and the class of hypothesis tests defined above. Then, given any $\alpha \in (0,1)$, local power at $\bfmu \neq {\bf 0}_p$ for the level-$\alpha$ test  based on $T_{n,w}$ is maximum when $w(\bfZ_1) = c$, a constant independent of $\bfZ_1$.
\end{Proposition}
%
\noindent This essentially means that power-wise the (unweighted) spatial sign test \citep{OjaBook10} is optimal in the given class of hypothesis tests when the data comes from a spherically symmetric distribution. Our simulations show that this empirically holds for non-spherical but elliptic distributions as well.

@@

The sample weighted spatial median $\hat\bfmu_w$ is a $\sqrt n$-consistent estimator of $\bfmu_w$, with the following result gives its asymptotic distribution:
%
\begin{Theorem}
Let $\bfA_w, \bfB_w$ be two matrices, dependent on the weight function $w$ such that
%
$$
\bfA_w = \BE \left[ \frac{w( \bfepsilon ) }{\| \bfepsilon \|} \left( 1 - \frac{\bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right) \right];
\quad
\bfB_w = \BE \left[ \frac{(w( \bfepsilon ))^2 \bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right]
$$
%
where $\bfepsilon \sim \mathcal E({\bf 0}, \Sigma, g)$. Then
%
\begin{equation}
\sqrt n (\hat\bfmu_w - \bfmu_w) \leadsto \cN_p ({\bf 0}, \bfA_w^{-1} \bfB_w \bfA_w^{-1})
\end{equation}
\end{Theorem}
%

%We provide a sketch of its proof in the supplementary material, which generalizes equivalent results for the spatial median \citep{OjaBook10}. 
Setting $w(\bfepsilon)=1$ above yields the asymptotic covariance matrix for the spatial median. Following this, the asymptotic relative efficiency (ARE) of $\bfmu_w$ corresponding to some non-uniform weight function with respect to the spatial median, say $\bfmu_s$ will be:
%
$$
ARE( \bfmu_w, \bfmu_s) = \left[ \frac{\text{det} (\bfA^{-1} \bfB \bfA^{-1})}{\text{det} ( \bfA_w^{-1} \bfB_w \bfA_w^{-1})} \right]^{1/p}
$$
%
with $\bfA = \BE [ 1/ \| \bfepsilon \| ( I_p - \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ) ]$ and $\bfB = \BE [ \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ]$. This is further simplified under spherical symmetry:

\begin{Corollary}
For the spherical distribution $\mathcal{E}(\bfmu, k \bfI_p, g); k \in \mathbb R, \bfmu \in \mathbb R^p$, we have
%
$$
ARE( \bfmu_w, \bfmu_s) = \frac{ \left[ \BE \left( \frac{f(r)}{r} \right) \right]^2}{\BE f^2(r) \left[ \BE \left( \frac{1}{r} \right) \right]^2 }
$$
\end{Corollary}
%
\begin{table}[t]
	\centering
    \begin{tabular}{c|ccccc}
    \hline
    & $t_3$   & $t_5$   & $t_{10}$  & $t_{20}$  & Normal \\ \hline
    $p=5$    & 1.28 & 1.20 & 1.16 & 1.14 & 1.13   \\
    $p=10$   & 1.15 & 1.10 & 1.07 & 1.07 & 1.06   \\
    $p=20$   & 1.09 & 1.05 & 1.04 & 1.03 & 1.03   \\
    $p=50$   & 1.05 & 1.02 & 1.01 & 1.01 & 1.01   \\ \hline
    \end{tabular}
    \caption{Table of $ARE(\bfmu_w; \bfmu_s)$ for different spherical distributions}
    \label{table:AREtablewsm}
\end{table}
%
Table \ref{table:AREtablewsm} summarizes the AREs for several families of elliptic distributions, numerically calculated using 10,000 random samples, and taking $f(r) = 1/(1+r)$. It is evident from the table that the weighted spatial median outperforms its unweighted counterpart for all data dimensions and distribution families. While the performance is much better for small values of $p$, weighting the signs seems to have less and less effect as $p$ grows larger. Assuming a first-order autoregressive (AR(1)) covariance structure, i.e. $\sigma_{ij} = \rho^{|i-j|}$ with $ \rho \in (0,1)$, results in largely similar ARE values as those obtained in table \ref{table:AREtablewsm} that assume $\Sigma = \bfI_p$.

@@

Under mild regularity conditions in the lines of \cite{WangPengLi15}, the following results hold for our generalized test statistic $C_{n,w}$ under $H_0$ as $n,p \rightarrow \infty$:
%
\begin{equation}\label{eqn:hdtest1}
\frac{C_{n,w}}{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\bfB_w^2)}} \leadsto N(0,1),
\end{equation}
%
and under contiguous alternatives $H_1: \bfmu = \bfmu_0$,
%
\begin{equation}\label{eqn:hdtest2}
\frac{C_{n,w} - \frac{n(n-1)}{2} \bfmu_0^T \bfA_w^2 \bfmu_0 (1 + o(1)) }{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\bfB_w^2)}} \leadsto N(0,1).
\end{equation}
%
We provide the details behind deriving these two results in the supplementary material, which extend the results of \cite{WangPengLi15} in a weightd sign setup using modified regularity conditions.

Following this, the ARE of this test statistic with respect to its unweighted version, i.e. the WPL statistic, is expressed as:
%
$$
ARE(C_{n,w}, \text{WPL}; \bfmu_0) = \frac{\bfmu_0^T \bfA_w^2 \bfmu_0}{\bfmu_0^T \bfA^2 \bfmu_0} \sqrt\frac{\text{Tr}(\bfB^2)}{\text{Tr}(\bfB_w^2)} (1 + o(1)),
$$
%
when $\Sigma = k \bfI_p$, this again simplifies to $\BE^2(f(r)/r)/[\BE f^2(r). \BE^2(1/r)]$. Thus the ARE values are exactly same as those in Table \ref{table:AREtablewsm}, indicating that for large data dimensions the WPL test and that based on $C_{n,w}$ are almost equivalent.

@@

\begin{table}
\centering
    \begin{tabular}{cc|ccc}\hline
\multicolumn{5}{l}{$\bfmu = \text{rep}(.15,p)$}\\\hline 
 $p$  & $n$    & CQ   & WPL  & $C_{n,w}$ \\\hline 
  500 & 20 & 0.051 & 0.376 & 0.418 \\
  500 & 50 & 0.060 & 0.832 & 0.866 \\
 1000 & 20 & 0.044 & 0.541 & 0.584 \\
 1000 & 50 & 0.039 & 0.973 & 0.987 \\\hline
\multicolumn{5}{l}{$\bfmu = \text{rep}(0,p)$}\\\hline
 $p$  & $n$    & CQ   & WPL  & $C_{n,w}$ \\\hline 
  500 & 20 & 0.049 & 0.061 & 0.063 \\
  500 & 50 & 0.039 & 0.061 & 0.064 \\
 1000 & 20 & 0.042 & 0.060 & 0.063 \\
 1000 & 50 & 0.043 & 0.050 & 0.050 \\\hline
    \end{tabular}
    \caption{Table of empirical powers of level-0.05 tests for the Chen and Qin (CQ), WPL and $C_{n,w}$ statistics}
    \label{table:AREtablehd}
\end{table}

>>>>

\vspace{1em}
\noindent{\bf (A1)} The weights are affine invariant, i.e.
%
$$
w(\bfA \bfx + \bfb, \bfA \BF + \bfb) = w(\bfx, \BF)
$$
%
for any $\bfb \in \BR^p$ and full rank matrix $\bfA \in \BR^{p \times p}$.

@@

A straightforward use of weighted signs in a location problem is to construct an outlier-robust alternative to the Hotelling's $T^2$ test using their sample mean vector and covariance matrix. Formally, this means testing for $H_0: \bfmu = {\bf 0}_p$ vs. $H_1:\bfmu \neq {\bf 0}_p$  based on the test statistic:
%
$$
T_{n,w} = n \bar\bfx_w^T ( \BS (\BX_w))^{-1} \bar\bfx_w,
$$
%
with $\bar\bfx_w = \sum_{i=1}^n \bfx_{w,i}/n, \bfx_{w,i} = w(\bfx_i ) \bfS (\bfx_i)$ for $i=1,2,...,n$, and $\BX_w = (\bfx_{w,1}, \ldots, \bfx_{w,n})^T$. However, the following holds true for this weighted sign test:
%
\begin{Proposition}\label{proposition:SignTest}
Consider $n$ random variables $\bfZ_1,...,\bfZ_n$ distributed independently and identically as $\mathcal{E}( \bfmu, k \bfI_p, g); k \in \mathbb R$, and the class of hypothesis tests defined above. Then, given any $\alpha \in (0,1)$, local power at $\bfmu \neq {\bf 0}_p$ for the level-$\alpha$ test  based on $T_{n,w}$ is maximum when $w(\bfZ_1) = c$, a constant independent of $\bfZ_1$.
\end{Proposition}
%
\noindent This essentially means that power-wise the (unweighted) spatial sign test \citep{OjaBook10} is optimal in the given class of hypothesis tests when the data comes from a spherically symmetric distribution. Our simulations show that this empirically holds for non-spherical but elliptic distributions as well.

@@

The sample weighted spatial median $\hat\bfmu_w$ is a $\sqrt n$-consistent estimator of $\bfmu_w$, with the following result gives its asymptotic distribution:
%
\begin{Theorem}
Let $\BA_w, \BB_w$ be two matrices, dependent on the weight function $w$ such that
%
$$
\BA_w = \BE \left[ \frac{w( \bfepsilon ) }{\| \bfepsilon \|} \left( 1 - \frac{\bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right) \right];
\quad
\BB_w = \BE \left[ \frac{(w( \bfepsilon ))^2 \bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right],
$$
%
where $\bfepsilon \sim \mathcal E({\bf 0}, \Sigma, g)$. Then
%
\begin{equation}
\sqrt n (\hat\bfmu_w - \bfmu_w) \leadsto \cN_p ({\bf 0}, \BA_w^{-1} \BB_w \BA_w^{-1}).
\end{equation}
\end{Theorem}
%

%We provide a sketch of its proof in the supplementary material, which generalizes equivalent results for the spatial median \citep{OjaBook10}. 
Setting $w(\bfepsilon)=1$ above yields the asymptotic covariance matrix for the spatial median. Following this, the asymptotic relative efficiency (ARE) of $\bfmu_w$ corresponding to some non-uniform weight function with respect to the spatial median, say $\bfmu_s$ will be:
%
$$
ARE( \bfmu_w, \bfmu_s) = \left[ \frac{\text{det} ( \BA^{-1} \BB \BA^{-1})}{\text{det} ( \BA_w^{-1} \BB_w \BA_w^{-1})} \right]^{1/p}
$$
%
with $\BA = \BE [ 1/ \| \bfepsilon \| ( \BI_p - \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ) ]$ and $\BB = \BE [ \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ]$. This is further simplified under spherical symmetry:

\begin{Corollary}
For the spherical distribution $\mathcal{E}(\bfmu, k \bfI_p, g); k \in \mathbb R, \bfmu \in \mathbb R^p$, we have
%
$$
ARE( \bfmu_w, \bfmu_s) = \frac{ \left[ \BE \left( \frac{f(r)}{r} \right) \right]^2}{\BE f^2(r) \left[ \BE \left( \frac{1}{r} \right) \right]^2 }.
$$
\end{Corollary}
%
\begin{table}[t]
\centering
\begin{footnotesize}
\begin{tabular}{c|ccccc}
    \hline
    & $t_3$   & $t_5$   & $t_{10}$  & $t_{20}$  & Normal \\ \hline
    $p=5$    & 1.28 & 1.20 & 1.16 & 1.14 & 1.13   \\
    $p=10$   & 1.15 & 1.10 & 1.07 & 1.07 & 1.06   \\
    $p=20$   & 1.09 & 1.05 & 1.04 & 1.03 & 1.03   \\
    $p=50$   & 1.05 & 1.02 & 1.01 & 1.01 & 1.01   \\ \hline
\end{tabular}
\end{footnotesize}
\caption{Table of $ARE(\bfmu_w; \bfmu_s)$ for different spherical distributions}
\label{table:AREtablewsm}
\end{table}
%
Table \ref{table:AREtablewsm} summarizes the AREs for several families of elliptic distributions, numerically calculated using 10,000 random samples, and taking $f(r) = 1/(1+r)$. It is evident from the table that the weighted spatial median outperforms its unweighted counterpart for all data dimensions and distribution families. While the performance is much better for small values of $p$, weighting the signs seems to have less and less effect as $p$ grows larger. Assuming a first-order autoregressive (AR(1)) covariance structure, i.e. $\sigma_{ij} = \rho^{|i-j|}$ with $ \rho \in (0,1)$, results in largely similar ARE values as those obtained in table \ref{table:AREtablewsm} that assume $\Sigma = \bfI_p$.

@@

Under mild regularity conditions in the lines of \cite{WangPengLi15}, the following results hold for our generalized test statistic $C_{n,w}$ under $H_0$ as $n,p \rightarrow \infty$:
%
\begin{equation}\label{eqn:hdtest1}
\frac{C_{n,w}}{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\BB_w^2)}} \leadsto N(0,1),
\end{equation}
%
and under contiguous alternatives $H_1: \bfmu = \bfmu_0$,
%
\begin{equation}\label{eqn:hdtest2}
\frac{C_{n,w} - \frac{n(n-1)}{2} \bfmu_0^T \BA_w^2 \bfmu_0 (1 + o(1)) }{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\BB_w^2)}} \leadsto N(0,1).
\end{equation}
%
We provide the details behind deriving these two results in the supplementary material, which extend the results of \cite{WangPengLi15} in a weightd sign setup using modified regularity conditions.

Following this, the ARE of this test statistic with respect to its unweighted version, i.e. the WPL statistic, is expressed as:
%
$$
ARE(C_{n,w}, \text{WPL}; \bfmu_0) = \frac{\bfmu_0^T \BA_w^2 \bfmu_0}{\bfmu_0^T \BA^2 \bfmu_0} \sqrt\frac{\text{Tr}( \BB^2)}{\text{Tr}( \BB_w^2)} (1 + o(1)),
$$
%
when $\Sigma = k \BI_p$, this again simplifies to $\BE^2(f(r)/r)/[\BE f^2(r). \BE^2(1/r)]$. Thus the ARE values are exactly same as those in Table \ref{table:AREtablewsm}, indicating that for large data dimensions the WPL test and that based on $C_{n,w}$ are almost equivalent.

@@

\begin{table}
\centering
\begin{footnotesize}
\begin{tabular}{cc|ccc}\hline
\multicolumn{5}{l}{$\bfmu = \text{rep}(.15,p)$}\\\hline 
 $p$  & $n$    & CQ   & WPL  & $C_{n,w}$ \\\hline 
  500 & 20 & 0.051 & 0.376 & 0.418 \\
  500 & 50 & 0.060 & 0.832 & 0.866 \\
 1000 & 20 & 0.044 & 0.541 & 0.584 \\
 1000 & 50 & 0.039 & 0.973 & 0.987 \\\hline
\multicolumn{5}{l}{$\bfmu = \text{rep}(0,p)$}\\\hline
 $p$  & $n$    & CQ   & WPL  & $C_{n,w}$ \\\hline 
  500 & 20 & 0.049 & 0.061 & 0.063 \\
  500 & 50 & 0.039 & 0.061 & 0.064 \\
 1000 & 20 & 0.042 & 0.060 & 0.063 \\
 1000 & 50 & 0.043 & 0.050 & 0.050 \\\hline
\end{tabular}
\end{footnotesize}
\caption{Table of empirical powers of level-0.05 tests for the Chen and Qin (CQ), WPL and $C_{n,w}$ statistics}
\label{table:AREtablehd}
\end{table}
